Adapting the MVDR to a GPU for active sonar systems of different sizes.

### 2012-11-15 ASA2013/asa2013.tex
la2pdf commit - 2012:11:15	18:18:24	(Thu15.Nov)

\begin{abstract}
The MVDR adaptive beamformer has been shown to improve image quality in active sonar systems, but at a major computational expense. This is because the estimation and inversion of a spatial covariance matrix is required for each image pixel. We target this problem by altering and mapping the MVDR algorithm to a GPU, and suggest three different solutions depending on the system size.

>>>>

\title{Adapting the MVDR to a GPU for active sonar systems of different sizes.}

\begin{abstract}
The MVDR beamformer has been shown to improve active sonar image quality compared to conventional methods. Unfortunately, it is also significantly more computationally expensive because a spatial covariance matrix must be estimated and inverted for each image pixel. We target this challenge by altering and mapping MVDR to a GPU, and suggest three different solutions depending on the system size.
